Polynomial expansions of finite volume data in a cut cell context

### 2023-04-24 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
finished first draft of paper
took out the the conclusion I was expecting and I put in what
the data actually shows

  We discuss the mechanics of forming stable local polynomial
  expansions of finite volume data in the context of cut cell grids.
  We show that significant solvability issues can arise from certain weighting
  functions.    A very rudimentary but stable cell merger algorithm is
  presented as we present evidence that these solvability issues may be
  an artifact of small-cell instabilties.

@@

If we use grid volumes at this point, the volume fraction
\begin{equation*}
\kappa_\ibold \equiv V_\ibold/h^D$ 
\end{equation*}
can be arbitrarily small ($ 0 < \kappa <= 1$).   We can also choose to
merge small volumes with larger neighbors without formal loss of
accuracy. The simple merger we use is described in
described in appendix \ref{appendix::merge}.
When merged using this algorithm, $\kappa$ can be larger than $2^D$.

>>>>

  We discuss the mechanics of forming stable local polynomial
  expansions of finite volume data in the context of cut cell grids.
  We show that significant solvability issues can arise from certain weighting
  functions.    A very rudimentary but stable cell merger algorithm is
  presented as we show that these solvability issues are not 
  an artifact of small-cell instabilties.

@@

If we use grid volumes at this point, the volume fraction
\begin{equation*}
\kappa_\ibold \equiv V_\ibold/h^D 
\end{equation*}
can be arbitrarily small ($ 0 < \kappa <= 1$).   We can also choose to
merge small volumes with larger neighbors without formal loss of
accuracy. The simple merger we use is described in
described in appendix \ref{appendix::merger}.
When merged using this algorithm, $\kappa$ can be larger than $2^D$.
